The title

### 2023-04-19 doc/multiverse.Rmd
Change PA-volume back to unlogged.

## Without Log Transforming PA Volume

```{r}
tar_load(model_tables_by_age_nolog)
tar_load(purdy_pictures_by_age_nolog)
```

Based on preliminary modelling on a subset of the data, we chose to log transform the physical activity volume variable.
Below, we present the results had we not made this decision.
These results are all moderated by age, as this was our primary analysis.

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-nolog) and Figure \@ref(fig:sleep-by-volume-fig-nolog).

```{r sleep-outcomes-nolog}
papaja::apa_table(
  model_tables_by_age_nolog$sleep$data,
  caption = model_tables_by_age_nolog$sleep$caption,
  note = model_tables_by_age_nolog$sleep$note,
  col_spanners = model_tables_by_age_nolog$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-nolog, fig.cap = "Sleep metrics on Physical activity volume"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_pa_volume), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-duration-fig-nolog).

```{r pa-outcomes-nolog}
papaja::apa_table(
  model_tables_by_age_nolog$physical_activity$data,
  caption = model_tables_by_age_nolog$physical_activity$caption,
  note = model_tables_by_age_nolog$physical_activity$note,
  col_spanners = model_tables_by_age_nolog$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-nolog, fig.cap = "Physical activity by sleep duration"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_duration_lag), error = FALSE)
```

@@

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-nolog).

```{r PA-by-sleep-efficiency-fig-nolog, fig.cap = "Physical activity by sleep efficiency"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_efficiency_lag), error = FALSE)
```

@@

We estimated the effect of sleep onset on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-onset-fig-nolog).

```{r PA-by-sleep-onset-fig-nolog, fig.cap = "Physical activity by sleep onset"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_onset_lag), error = FALSE)
```

@@

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-nolog) and Figure \@ref(fig:PA-by-sleep-regularity-fig-nolog).

```{r PA-by-sleep-regularity-fig-nolog, fig.cap = "Physical activity by sleep regularity"}
knitr::include_graphics(here::here(purdy_pictures_by_age_nolog$predictor_sleep_regularity_lag), error = FALSE)
```

>>>>

## Log Transforming PA Volume

```{r}
tar_load(model_tables_by_age_log)
tar_load(purdy_pictures_by_age_log)
```

Based on preliminary modelling on a subset of the data, we chose to leave physical activity volume in its natural form to enhance interpretability. The log scale meant that the variable became unintepretable towards the edge of its range. Below, we present the results had we not made this decision. These results are all moderated by age, as this was our primary analysis. The associated figures are back-transformed to the scale range.

@@

We estimated the effects of physical activity on sleep (RQ1) using mixed-effects models.
We estimated the effect of physical activity volume on sleep by age, and the results are presented in Table \@ref(tab:sleep-outcomes-log) and Figure \@ref(fig:sleep-by-volume-fig-log).

```{r sleep-outcomes-log}
papaja::apa_table(
  model_tables_by_age_log$sleep$data,
  caption = model_tables_by_age_log$sleep$caption,
  note = model_tables_by_age_log$sleep$note,
  col_spanners = model_tables_by_age_log$sleep$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r sleep-by-volume-fig-log, fig.cap = "Sleep metrics on Physical activity volume"}
knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_pa_volume), error = FALSE)
```

@@

We estimated the effect of sleep duration on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-duration-fig-log).

```{r pa-outcomes-log}
papaja::apa_table(
  model_tables_by_age_log$physical_activity$data,
  caption = model_tables_by_age_log$physical_activity$caption,
  note = model_tables_by_age_log$physical_activity$note,
  col_spanners = model_tables_by_age_log$physical_activity$col_spanners,
  escape = FALSE,
  landscape = TRUE
)
```

```{r PA-by-sleep-duration-fig-log, fig.cap = "Physical activity by sleep duration"}
knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_duration_lag), error = FALSE)
```

@@

We estimated the effect of sleep efficiency on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-efficiency-fig-log).

```{r PA-by-sleep-efficiency-fig-log, fig.cap = "Physical activity by sleep efficiency"}
knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_efficiency_lag), error = FALSE)
```

@@

We estimated the effect of sleep onset on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-onset-fig-log).

```{r PA-by-sleep-onset-fig-log, fig.cap = "Physical activity by sleep onset"}
knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_onset_lag), error = FALSE)
```

@@

We estimated the effect of sleep regularity on physical activity by age.
Results, controlling for sex, SES, and BMI are presented in Table \@ref(tab:pa-outcomes-log) and Figure \@ref(fig:PA-by-sleep-regularity-fig-log).

```{r PA-by-sleep-regularity-fig-log, fig.cap = "Physical activity by sleep regularity"}
knitr::include_graphics(here::here(purdy_pictures_by_age_log$predictor_sleep_regularity_lag), error = FALSE)
```
